### 2014-01-31 analysis/Outline.rmd
Fixed glitches in outline.rmd

palette(alpha(rich.colors(4),0.5))
with(dfr, plot(log10(m.lf), log10(m.rf), 
               axes=FALSE,
               xlab="Aboveground biomass (kg)",
               ylab="Foliage mass (kg)",
               type='n',col=pft, panel.first={
                 for(z in c(0.05, 0.25, 0.5, 0.75, 1))abline(log10(z),1)
               }))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
for(i in 1:3)plot(sm[[i]], add=TRUE, col=palette()[i], type='l', lwd=2)
box()
legend("bottomright", levels(dfr$pft), fill=alpha(palette(),1))

@@

```{r echo=FALSE, eval=FALSE}
# subset/refine data.
dfr <- droplevels(subset(data, !is.na(m.st) & !is.na(m.lf) & pft != "" & m.lf > 0))
dfr <- within(dfr, {
  dataset <- as.factor(dataset)
  species <- as.factor(species)
  pft <- as.factor(pft)
  m.lf.fraction <- with(dfr, m.lf / m.so)
  log_m.so <- log10(m.so)
  log_m.lf.fraction <- log10(m.lf.fraction)
})

with(dfr, plot(log_m.so, log_m.lf.fraction, axes=FALSE,
               xlab="Aboveground biomass (kg)",
               ylab="Leaf mass fraction (-)",
               pch=19, col=pft
))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
box()
legend("topright", levels(dfr$pft), pch=19, col=palette())
#Figure X. Much higher leaf mass fraction for evergreen gymnosperms at a given total aboveground plant biomass.
```

>>>>

palette(alpha(rich.colors(4),0.5))
with(dfr, plot(log10(m.lf), log10(m.rf), 
               axes=FALSE,
               xlab="Leaf mass (kg)",
               ylab="Fine root mass (kg)",
               type='n',col=pft, panel.first={
                 for(z in c(0.05, 0.25, 0.5, 0.75, 1))abline(log10(z),1)
               }))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
for(i in 1:3)plot(sm[[i]], add=TRUE, col=palette()[i], type='l', lwd=2)
box()
legend("bottomright", levels(dfr$pft), fill=alpha(palette(),1))

@@

```{r echo=FALSE, eval=TRUE}
# subset/refine data.
dfr <- droplevels(subset(data, !is.na(m.st) & !is.na(m.lf) & pft != "" & m.lf > 0))
dfr <- within(dfr, {
  dataset <- as.factor(dataset)
  species <- as.factor(species)
  pft <- as.factor(pft)
  m.lf.fraction <- with(dfr, m.lf / m.so)
  log_m.so <- log10(m.so)
  log_m.lf.fraction <- log10(m.lf.fraction)
})

with(dfr, plot(log_m.so, log_m.lf.fraction, axes=FALSE,
               xlab="Aboveground biomass (kg)",
               ylab="Leaf mass fraction (-)",
               pch=19, col=pft
))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
box()
legend("topright", levels(dfr$pft), pch=19, col=palette())

```
Figure X. Much higher leaf mass fraction for evergreen gymnosperms at a given total aboveground plant biomass.
